Fixing Vulnerabilities Hinders Maintainability

### 2019-02-04 paper/ICPC19/icpc19.tex
changing comprehends
swap misc
comtemplates

\end{lstlisting}
%
\section{Methodology}\label{sec:methodology}
%
The methodology used to measure the impact of security refactorings on the
maintainability of open-source software is discussed in this section. The
methodology comprehends the following steps, as illustrated in
Figure~\ref{fig:met}:

@@

    \item \textbf{Miscellaneous} This pattern comprises several other categories
    of security refactorings (e.g., \textit{path traversal and buffer
    overflow}). It contains several other security refactorings that do not have
    their own pattern yet. The patterns not satisfying the size requirement of
    more than $20$ refactorings are contemplated here: \textit{Resource Leak},
    \textit{SHA-1 Hash Function}, \textit{Broken Access Control},
    \textit{Sensitive Data Exposure}, \textit{Insufficient Attack Protection},
    \textit{Overflow}, \textit{Path Traversal}.

@@

    \item \textbf{Memory Leak.} Memory management issue found more frequently in
    programming languages that do not manage memory automatically (e.g., C/C++
    and Objective-C), i.e., where instead developers are responsible for
    handling it. One of the main causes of DoS attacks.
\end{itemize}

@@

The dataset contemplates security flaws for more than $13$ different languages
being PHP ($39\%$) and C ($24\%$) the most prevalent ones; see Figure~\ref{fig:lang}.
To classify the applications in the dataset, we use a taxonomy for open-source
software from previous work~\cite{7816479}. Figure~\ref{fig:domain}
presents the projects domain distribution: \textit{Aplication Software} ($25$),
software that provides end-users with functional systems; \textit{Web libraries
and frameworks} ($20$); \textit{System Software} ($18$), software that provides
services and infrastructures (e.g., operating systems, servers and databases);
\textit{Software Tool} ($13$), software that supports development (e.g.,
programming languages, compilers, package managers, IDEs); and, \textit{Non-web
libraries and frameworks} ($18$), for desktop and mobile software.
%
Table~\ref{tab:dataset} presents the descriptive statistics of the $94$
open-source projects involved in this study, including the number of forks, the
number of stars, the number of watchers, the number of contributors, the number
of commits, the number of branches, the number of releases,  size (cf. GitHub it
is the size of the whole repository, including all of its history, in
kilobytes), the number of issues, and the number of pull requests.

>>>>

\end{lstlisting}
%
\section{Methodology}\label{sec:methodology}
%
The methodology used to measure the impact of security refactorings on the
maintainability of open-source software is discussed in this section. The
methodology is comprised of the following steps, as illustrated in
Figure~\ref{fig:met}:

@@

@@

    \item \textbf{Memory Leak.} Memory management issue found more frequently in
    programming languages that do not manage memory automatically (e.g., C/C++
    and Objective-C), i.e., where instead developers are responsible for
    handling it. One of the main causes of DoS attacks.

    \item \textbf{Miscellaneous} This pattern comprises several other categories
    of security refactorings (e.g., \textit{path traversal and buffer
    overflow}). It contains several other security refactorings that do not have
    their own pattern yet. The patterns not satisfying the size requirement of
    more than $20$ refactorings are contemplated here: \textit{Resource Leak},
    \textit{SHA-1 Hash Function}, \textit{Broken Access Control},
    \textit{Sensitive Data Exposure}, \textit{Insufficient Attack Protection},
    \textit{Overflow}, \textit{Path Traversal}.
\end{itemize}

@@

The dataset contains security flaws for more than $13$ different languages
being PHP ($39\%$) and C ($24\%$) the most prevalent ones; see Figure~\ref{fig:lang}.
To classify the applications in the dataset, we use a taxonomy for open-source
software from previous work~\cite{7816479}. Figure~\ref{fig:domain}
presents the projects domain distribution: \textit{Aplication Software} ($25$),
software that provides end-users with functional systems; \textit{Web libraries
and frameworks} ($20$); \textit{System Software} ($18$), software that provides
services and infrastructures (e.g., operating systems, servers and databases);
\textit{Software Tool} ($13$), software that supports development (e.g.,
programming languages, compilers, package managers, IDEs); and, \textit{Non-web
libraries and frameworks} ($18$), for desktop and mobile software.
%
Table~\ref{tab:dataset} presents the descriptive statistics of the $94$
open-source projects involved in this study, including the number of forks, the
number of stars, the number of watchers, the number of contributors, the number
of commits, the number of branches, the number of releases,  size (cf. GitHub it
is the size of the whole repository, including all of its history, in
kilobytes), the number of issues, and the number of pull requests.
